Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/paper.tex

Recall the rank factorisation property of the pseudo-inverse \citep{todo}: if $A=BC$ with $A\in\mathbb{R}^{m\times n}$ of rank $k$, $B\in\mathbb{R}^{m\times k}$ and $C\in\mathbb{R}^{k\times n}$, then $A^\dagger=C^\dagger B^\dagger$ and, since $C$ is full rank, $C^\dagger=C' (CC')^{-1}$.
%
Using this property on the minimal norm solution $\hat G$ yields
\begin{equation}
\begin{aligned}
X(FEX)^\dagger &=X((FK)(K'X))^\dagger \\
&=X(K'X)'((K'X)(K'X)')^{-1}(FK)^\dagger \\
&=(XX')K(K'XX'K)^{-1}(FK)^\dagger 
\end{aligned}
\end{equation}

@@

\section{Related works}
\subsection{back-to-back regression as a special case of canonical component analysis?}
Formula (1) shows that back-to-back regression may be related to canonical component analysis (CCA).
%
In CCA, we are given two matrices X and Y (or size N,p and N,q) that describe different features measured on the same data sample, and characterize their proximity (that is, between the subspaces spanned by their columns) as the correlation between linear combinations of X and Y.

>>>>

Recall the rank factorisation property of the pseudo-inverse \citep{todo}: if $A=BC$ with $A\in\mathbb{R}^{m\times n}$ of rank $k$, $B\in\mathbb{R}^{m\times k}$ and $C\in\mathbb{R}^{k\times n}$, then $A^\dagger=C^\dagger B^\dagger$ and, since $C$ is full rank, $C^\dagger=C' (CC')^{-1}$.
%
Using this property on the minimal norm solution $\hat G$ yields
\begin{equation}
\begin{aligned}
(XEF)^\dagger X&=((XK')(KF))^\dagger X\\
&=(FK)^\dagger (XK')'((XK')(XK')')^{-1} X\\
&=(FK)^\dagger KX' (K'XX'K)^{-1} X
\end{aligned}
\end{equation}

@@

\section{Related works}
\subsection{Back-to-back regression as a special case of canonical component analysis}
Formula (1) shows that back-to-back regression may be related to canonical component analysis (CCA).
%
In CCA, we are given two matrices X and Y (or size N,p and N,q) that describe different features measured on the same data sample, and characterize their proximity (that is, between the subspaces spanned by their columns) as the correlation between linear combinations of X and Y.
